---
title: "test_tq_Rblpapi_bds"
output: github_document
author: 'Art Steinmetz'
---
# testing Tidyquant Rblpapi integration

validate some variations on <code>bds()</code>

```{r}
devtools::install_github("business-science/tidyquant")
library(tidyverse)
library(stringr)
library(dplyr)
library(lubridate)
library(Rblpapi)
library(tidyquant)
library(reprex)
library(Rblpapi)

paste("Using tidyquant version",packageVersion('tidyquant'))

```

#initial test
# from Rblpapi docs using Rblpapi::bdp(), not tq_get()
```{r}
# Get BBG Descriptive Data
## Not run:
## simple query
blpConnect()
output_bds<-bds("GOOG US Equity", "TOP_20_HOLDERS_PUBLIC_FILINGS")
output_bds
```

#using tq_get
The parameter names for bds() differ slightly from bdp() and bdh().
<code>securities</code> becomes <code>security</code> and that blows up piping in the ticker symbols.   <code>fields</code> becomes <code>field</code> 


#Pipe in first parameter with the ticker
```{r}
my_bloomberg_data <- c('GOOG US Equity') %>%
    tq_get(get         = "rblpapi",
           rblpapi_fun = "bds",
           field     = c("TOP_20_HOLDERS_PUBLIC_FILINGS")
           )

```

#try assigning x.
```{r}
my_bloomberg_data <-  tq_get(x = 'GOOG US Equity',
                             get = "rblpapi",
                             rblpapi_fun = "bds",
                             field = c("TOP_20_HOLDERS_PUBLIC_FILINGS")
           )

my_bloomberg_data
```

Commented out because otherwise execution halts.  Error message shown below.

```{r}
# my_bloomberg_data <-  tq_get(security = 'GOOG US Equity',
#                             get = "rblpapi",
#                             rblpapi_fun = "bds",
#                             field = c("TOP_20_HOLDERS_PUBLIC_FILINGS")
#           )


```
`Error in tq_get(security = "GOOG US Equity", get = "rblpapi", rblpapi_fun = "bds",  : 
  argument "x" is missing, with no default`
  
