---
title: "test_tq_Rblpapi"
output: github_document
author: 'Art Steinmetz'
---
# testing Tidyquant Rblpapi integration

validate some variations on <code>bdh()</code>

```{r}
devtools::install_github("business-science/tidyquant")
library(tidyverse)
library(stringr)
library(dplyr)
library(lubridate)
library(Rblpapi)
library(tidyquant)
library(reprex)

```

initial test
```{r}
my_bloomberg_data <- c('SPX Index','AGTHX Equity') %>%
    tq_get(get         = "rblpapi",
           rblpapi_fun = "bdh",
           fields      = c("PX_LAST","TOT_RETURN_INDEX_GROSS_DVDS"),
           options     = c("periodicitySelection" = "MONTHLY"),
           from        = "2016-01-01",
           to          = "2016-12-31")
my_bloomberg_data
```

Use `start.date` and 'end.date' instead of `from/to`
```{r}
my_bloomberg_data <- c('SPX Index','AGTHX Equity') %>%
    tq_get(get         = "rblpapi",
           rblpapi_fun = "bdh",
           fields      = c("PX_LAST","TOT_RETURN_INDEX_GROSS_DVDS"),
           options     = c("periodicitySelection" = "MONTHLY"),
           start.date        = as.Date("2016-01-01"),
           end.date          = as.Date("2016-12-31")
           )
           

my_bloomberg_data
```


```{r}
#single security, single field bdh
my_bloomberg_data <- c('SPX Index') %>%
    tq_get(get         = "Rblpapi",
           rblpapi_fun = "bdh",
           fields      = c("PX_LAST"),
           options     = c("periodicitySelection" = "MONTHLY"),
           from        = "2016-01-01",
           to          = "2016-12-31"
           )
           

my_bloomberg_data
```
# does omission of 'to' field default to sys.date?
```{r}
# does omission of 'to' field default to sys.date?
my_bloomberg_data <- c('SPX Index') %>%
    tq_get(get         = "Rblpapi",
           rblpapi_fun = "bdh",
           fields      = c("PX_LAST"),
           options     = c("periodicitySelection" = "MONTHLY"),
           from        = "2017-01-01"
           )
           

my_bloomberg_data
```
Yes, it does!


#Vary periodicity
```{r}
#vary periodicity
my_bloomberg_data <- c('SPX Index','ODMAX Equity') %>%
    tq_get(get         = "Rblpapi",
           rblpapi_fun = "bdh",
           fields      = c("PX_LAST"),
           options     = c("periodicitySelection" = "WEEKLY"),
           from        = "2016-01-01",
           to          = "2016-12-31"
           )
           

my_bloomberg_data
```
```{r}
#vary periodicity
my_bloomberg_data <- c('SPX Index','ODMAX Equity') %>%
    tq_get(get         = "Rblpapi",
           rblpapi_fun = "bdh",
           fields      = c("PX_LAST"),
           options     = c("periodicitySelection" = "DAILY"),
           from        = "2016-01-01",
           to          = "2016-12-31"
           )
           

my_bloomberg_data
```
#mix sec types
```{r}
#mix sec types
my_bloomberg_data <- c('GT10 Govt','ODMAX Equity') %>%
    tq_get(get         = "Rblpapi",
           rblpapi_fun = "bdh",
           fields      = c("PX_LAST"),
           options     = c("periodicitySelection" = "DAILY"),
           from        = "2016-01-01",
           to          = "2016-3-30"
           )
           

my_bloomberg_data
```
#show that sectype dates don't align due to varying holidays
# not in scope of tidyquant

```{r}
#show that sectype dates don't align due to varying holidays
# not in scope of tidyquant
my_bloomberg_data %>% 
  spread(symbol,PX_LAST) %>% 
  filter(is.na(`ODMAX Equity`))

```

#try some overrides from Rblpapi documentation
```{r}
#try some overrides from Rblpapi documentation
## example for an options field: request monthly data; see section A.2.4 of
## http://www.bloomberglabs.com/content/uploads/sites/2/2014/07/blpapi-developers-guide-2.54.pdf
## for more
opt <- c("periodicitySelection"="MONTHLY")
start.date=Sys.Date()-31*6

my_bloomberg_data <- c('SPY US Equity') %>%
    tq_get(get         = "Rblpapi",
           rblpapi_fun = "bdh",
           fields      = c("PX_LAST", "VOLUME"),
           options     = opt,
           from        = start.date
           )
           
my_bloomberg_data
```
##demonstrate that override parameter works as intended
```{r}

## example for options and overrides
opt <- c("periodicitySelection" = "QUARTERLY")
ovrd <- c("BEST_FPERIOD_OVERRIDE"="1GQ")
start.date=Sys.Date()-365.25
         
#no override
my_bloomberg_data <- c('IBM US Equity') %>%
    tq_get(get         = "Rblpapi",
           rblpapi_fun = "bdh",
           fields      = c("BEST_SALES"),
           options     = opt,
           #overrides   = ovrd,
           from        = start.date
           ) %>% 
  mutate(Override="No")

#with override
my_bloomberg_data <- c('IBM US Equity') %>%
    tq_get(get         = "Rblpapi",
           rblpapi_fun = "bdh",
           fields      = c("BEST_SALES"),
           options     = opt,
           overrides   = ovrd,
           from        = start.date
           ) %>% 
  mutate(Override="Yes") %>% 
  bind_rows(my_bloomberg_data)

#should show the effect of this override
my_bloomberg_data
```
